---
title: "homework9"
author: "Wei Hern Lim"
date: "3/30/2022"
output: html_document
---

# Team Members:
- Michael Mila
- Wei Hern Lim

Github: https://github.com/mmila38/practice4

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
```

```{r}
av <- read.csv("https://raw.githubusercontent.com/fivethirtyeight/data/master/avengers/avengers.csv", stringsAsFactors = FALSE)
```

```{r}
#parsing time and deaths[1-5] into one column
av0 = av %>% filter(Name.Alias != "")
av0 = av0 %>% filter(Name.Alias != "Vance Astrovik")
av1 = av0 %>% gather(time, deaths, c(11, 13, 15, 17, 19))
# replacing death[number] with number and empty characters with NA
av1 = av1 %>% mutate(time = parse_number(time))
av1 = av1 %>% mutate(Deaths = replace(deaths, deaths == "", NA)) %>%
select(-deaths)
av2 = av1 %>% select(Name.Alias, time, Deaths)
av3 = av %>% gather(key = time, value = Return, c(12, 14, 16, 18, 20))
av3 = av3 %>% mutate(time = parse_number(time))
av4 = av3 %>% select(Name.Alias, time, Return)
av.neat = left_join(av2, av4, by = c("Name.Alias", "time"))
av.neat$Return = replace(av.neat$Return, av.neat$Return == "", NA)
```

## Michael's Question: But you can only tempt death so many times. There’s a 2-in-3 chance that a member of the Avengers returned from their first stint in the afterlife, but only a 50 percent chance they recovered from a second or third death.

```{r}
## characters who have died once
av.test = av.neat %>% filter(Deaths == "YES", time == 1)
av.test1 = av.test %>% mutate(firstDeathReturn = (Return == "YES"))
mean(av.test1$firstDeathReturn)
```

### The return percentage after the first death is about 0.70 or 70%. So the article is kind of correct in saying that there is a 2-in-3 chance that a member returns after the first death.

```{r}
# characters who have died 2 or 3 times
av.test = av.neat %>% filter(Deaths == "YES", time %in% c(2, 3))
av.test1 = av.test %>% mutate(firstDeathReturn = (Return == "YES"))
mean(av.test1$firstDeathReturn)
```

### The return percentage after the second or third is about 0.53 or 53%. Again, the article is somewhat correct in saying that there is a 50% recover after their second or third death.

### Wei Hern's Question: The MVP of the Earth-616 Marvel Universe Avengers has to be Jocasta — an android based on Janet van Dyne and built by Ultron — who has been destroyed five times and then recovered five times.

```{r} 
av.test2 = av.neat %>% filter(Deaths == "YES", Return == "YES") %>% arrange(desc(time))
av.test3 = av.neat %>% filter(time == 2, Deaths == "YES")
av.test3 = av.test3 %>% mutate(Returned = (Return == "YES"))
mean(av.test3$Returned)
View(av.test3)
```

### It seems that no one else comes close to Jocasta in terms of number of times they have returned. The next person in the list would have only returned two times compared to Jocasta's five times. Out of the people who have died twice, only 53% of the people ended up returning.

