---
title: "homework9"
author: "Michael Mila"
date: "3/30/2022"
output: html_document
---

# Team Members:
- Michael Mila
- Wei Hern Lim

Github: https://github.com/mmila38/practice4

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
```

```{r}
av <- read.csv("https://raw.githubusercontent.com/fivethirtyeight/data/master/avengers/avengers.csv", stringsAsFactors = FALSE)
```

```{r}

#parsing time and deaths[1-5] into one column
av0 = av %>% filter(Name.Alias != "")
av0 = av0 %>% filter(Name.Alias != "Vance Astrovik")
av1 = av0 %>% gather(time, deaths, c(11, 13, 15, 17, 19))

# replacing death[number] with number and empty characters with NA
av1 = av1 %>% mutate(time = parse_number(time))
av1 = av1 %>% mutate(Deaths = replace(deaths, deaths == "", NA)) %>%
select(-deaths)

av2 = av1 %>% select(Name.Alias, time, Deaths)
av3 = av %>% gather(key = time, value = Return, c(12, 14, 16, 18, 20))
av3 = av3 %>% mutate(time = parse_number(time))
av4 = av3 %>% select(Name.Alias, time, Return)

av.neat = left_join(av2, av4, by = c("Name.Alias", "time"))
av.neat$Return = replace(av.neat$Return, av.neat$Return == "", NA)
```

## Michael's Question: But you can only tempt death so many times. There’s a 2-in-3 chance that a member of the Avengers returned from their first stint in the afterlife, but only a 50 percent chance they recovered from a second or third death.

```{r}
## characters who have died once
av.test = av.neat %>% filter(Deaths == "YES", time == 1)
av.test1 = av.test %>% mutate(firstDeathReturn = (Return == "YES"))
mean(av.test1$firstDeathReturn)
```

### The return percentage after the first death is about 0.70 or 70%. So the article is kind of correct in saying that there is a 2-in-3 chance that a member returns after the first death.

```{r}
# characters who have died 2 or 3 times
av.test = av.neat %>% filter(Deaths == "YES", time %in% c(2, 3))
av.test1 = av.test %>% mutate(firstDeathReturn = (Return == "YES"))
mean(av.test1$firstDeathReturn)
```

### The return percentage after the second or third is about 0.53 or 53%. Again, the article is somewhat correct in saying that there is a 50% recover after their second or third death.

